\documentclass[final, leqno]{ukthesis}

\usepackage[table]{xcolor}

\usepackage[pdfauthor={Joel Klipfel},
            pdftitle={The Direct Scattering Map for the 
            	Intermediate Long Wave Equation},
            pdfsubject={Inverse Scattering},
            pdfkeywords={Inverse Scattering Transform, Inverse Scattering, Intermediate Long Wave Equation, Dispersive Waves, Diffeo-Integral Equations, Partial Differential Equations},
            pdfproducer={Latex with hyperref},
            pdfcreator={latex->dvips->ps2pdf},
            pdfpagemode=UseOutlines,
            bookmarksopen=true,
            letterpaper,
            bookmarksnumbered=true]{hyperref}
\usepackage{memhfixc}
\usepackage{multirow}

\include{header.uk-dissertation}
% \input{NewCenturyLikeFont}

% \DeclareSymbolFont{myletters}{OML}{ztmcm}{m}{it}
% \DeclareMathSymbol{\lambda}{\mathord}{myletters}{"15}
% \usepackage{newtxtext,newtxmath}

% \setmainfont{Times New Roman}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\numberwithin{equation}{chapter}

\def\chzerotitle{INTRODUCTION}
\def\chzeroloc{Chapter0-Intro/Chapter0-Intro.tex}

\def\chonetitle{GREEN'S FUNCTIONS: LOWER BOUNDARY VALUES}
\def\choneloc{Chapter1-GF/Chapter1-GF.tex}

\def\chtwotitle{GREENS FUNCTIONS: MAPPING PROPERTIES}
\def\chtwoloc{Chapter2-GFmapping/Chapter2-GFmapping.tex}

\def\chthreetitle{GREEN'S FUNCTIONS: ANALYTIC CONTINUATION}
\def\chthreeloc{Chapter3-xContin/Chapter3-xContin.tex}

\def\chfourtitle{JOST SOLUTIONS \& THE DIRECT SCATTERING MAP}
\def\chfourloc{Chapter4-Jost/Chapter4-Jost.tex}

\def\apploc{Appendices/Appendices}

\def\bibloc{Bibliography/dissertation.bibliography}

\def\vitaloc{vita.tex}


\begin{document}
% \blindtext
%author data
\author{Joel Klipfel}
\title{\MakeUppercase{THE DIRECT SCATTERING MAP FOR THE INTERMEDIATE LONG WAVE EQUATION}}
% \include{Abstract/abstract.tex}
\abstract{
	In the early 1980's, Kodama, Ablowitz and Satsuma, together with Santini, 
	Ablowitz and Fokas, 
	developed the formal inverse scattering theory of the 
	Intermediate Long Wave (ILW) equation and explored its connections with 
	the Benjamin-Ono (BO) and KdV equations. 
	The ILW equation
	\begin{align*}
		u_t + \frac{1}{\delta} u_x + 2 u u_x + Tu_{xx} = 0, 
	\end{align*}
	models the behavior of long internal gravitational waves in stratified fluids of 
	depth
	$0< \delta < \infty$, where $T$ is a singular operator which depends 
	on the depth $\delta$.
	In the limit 
	$\delta \to 0$, the ILW reduces to the Korteweg de Vries (KdV) equation, and in the 
	limit $\delta \to \infty$, the ILW (at least formally) reduces to the Benjamin-Ono (BO) 
	equation. 

	While the KdV
	equation is very well understood, a rigorous analysis of inverse scattering for the 
	ILW equation remains to be accomplished. There
	is currently no rigorous proof that the Inverse Scattering Transform
	outlined by Kodama \textit{et al.} solves the ILW, even for small data.
	In this dissertation, we seek to help ameliorate this gap in knowledge
	by presenting a mathematically rigorous construction
	of the direct scattering map for the ILW's Inverse Scattering Transform.
}

\advisor{Peter Perry}
\keywords{Inverse Scattering Transform, Inverse Scattering, Intermediate Long Wave Equation, Dispersive Waves, Diffeo-Integral Equations, Partial Differential Equations}
\dgs{Ben Braun}
\orcidaddress{https://orcid.org/0000-0002-4135-2753}
%the title pages
\frontmatter
\maketitle
\begin{dedication}
	To the University of Kentucky Graduate Student Congress, whose community of graduate students, 
	professional students and postdocs helped sustain me through the myriad challenges of 
	graduate school.
\end{dedication}
\begin{acknowledgments}
	Throughout my graduate career, I benefited immensely from the care, support and 
	sage guidance from a great many kind souls. In particular, I wish to thank my advisor, 
	Professor Peter Perry, and our collaborator from the University of Oklahoma for
	their patience and enthusiasm in sharing their great mathematical wisdom with me.
	I also wish to acknowledge my committee members, Professors Sumit Das, Lawrence 
	Harris, Peter Hislop, and Ribhu Kaul for their continual support throughout my 
	time at the University of Kentucky (UK), and thank Professor Zhognwei Shen 
	for the many stimulating mathematical discussions.

	Reflecting on my time at the UK, I find it hard to overstate 
	how much I received from my interactions from the math department's amazing 
	staff, Rejeana Cassady, Christine Levitt, and Sheri Rhine. I long ago lost 
	track of the number of times they each went out of their way to help and 
	support me, and they each had their own unique ways to make me feel that 
	I could somehow make through the program at times when I felt less
	than optimistic about my future in the department. Rejeana, Christine, Sheri,
	Thank you.

	Few, I think, will dispute that graduate school is, in the best circumstances,
	a trying experience. Graduate school would have been almost unimaginably 
	more difficult without support and advice from numerous members
	of the UK Graduate Student Congress (GSC) and members of the 
	broader UK community. While there are far too many of you in the GSC and 
	UK communities who have supported me for me to list you all here, you know who 
	you are, and I do wish to extend a very special thank you to all of you. 
	Additionally, I wish to specifically acknowledge how much I have personally 
	benefited from the life affirming work of Dr. Morris Grubbs, Dr. James Lincoln, 
	and Carol Taylor-Shim. Whatever UK pays you, it is no where close to what you 
	deserve.

	Saving the most important acknowledgment for last, I have my brilliant and
	talented life partner, Dr. Nandita Sahajpal, to thank for getting me through
	graduate school. Over the past several years, she has done more for me 
	that I can ever adequately thank her for, and I would not be here today
	without her. I will always treasure our late night discussions about math
	and a great many other topics, and I am beyond fortunate she has chosen to 
	share her life with me.
\end{acknowledgments}

\begin{KeepFromToc}
	\tableofcontents\clearpage
\end{KeepFromToc}
\listoffigures\clearpage
% \listoftables\clearpage
%----------------------------------------------




\mainmatter


\begin{DoubleSpace}

%========================
% Chapter 0: Introduction
%========================
\subfile{\chzeroloc}


%%===================================================
%% Chapter 1: Green's Function: Lower Boundary Values
%%===================================================
\subfile{\choneloc}


%%=================================================
%% Chapter 2: Green's Functions: Mapping Properties
%%=================================================
\subfile{\chtwoloc}

%%====================================================
%% Chapter 3: Green's Functions: Analytic Continuation
%%====================================================
\subfile{\chthreeloc}


%%=======================================================
%% Chapter 4: JOST SOLUTIONS \& THE DIRECT SCATTERING MAP
%%=======================================================
\subfile{\chfourloc}


\end{DoubleSpace}

%-----------------------------------------------
\backmatter

%%=========
%% Appendix
%%=========
\begin{theappendices}
	\subfile{\apploc}
\end{theappendices}

% \emph{testing emph} \textit{testing textit}

% \renewcommand{\emph}[1]{\textit{#1}}

\bibliographystyle{plain}
\bibliography{\bibloc}
\nocite{*}


\chapter{Vita}
\subfile{\vitaloc}

\end{document}